Lightweight Scheduling for the PRAGMA Cloud Testbed

### 2016-07-14 paper.tex
Add notes from call

\textbf{Developed and used a PCC stub:}  To provide an interface for managing virtual cluster, we used a simple stub to emulate the functionality of PCC.  The stub serves as a generic interface; it is a small Python script called \textit{pcc-check-reservations} that polls PRAGMA Booking via its REST interface and monitors reservations.  Once it finds a reservation that needs to be activated, it launches pragma\_boot via SSH.  It does not  monitor the virtual cluster nor does it email the users when their reservation are about to expire.

@@

\begin{itemize}
\item Added the ability to make multiple reservations on a resource per time slot to allow more than one virtual cluster to run simultaneously on a site.   This was the most extensive change we made to Booked.  Fortunately, no changes were needed to the backend database but it required several changes to the GUI code to allow an additional reservation to be made on a resource and to display multiple reservations per time slot in the calendar views.  In total, enhancements were made to seven PHP files and two template files.
\item Added a custom field for a public SSH key  to the user profile.  When PCC launches a virtual cluster, it pulls the public SSH key from the user's  profile and gives it to pragma\_boot so that the user can login as root once the virtual cluster is launched.   The ability to use a root login is not required for all but can be needed in some case if users want to do system modifications. A user with a root login has a full ownership of the virtual cluster. 
\item Added custom fields for CPU count, amount of memory per host, and virtual cluster image name to the reservation specification.
\item Added custom fields for CPU count, amount of memory per host, site hostname, and ENT capability (enabled, disabled) to the resource specification.
\item Added a numeric count as a custom field type.  Booked only provided text matching on search so if a host had 16 CPUs available and the user requested 8 CPUs, the search would fail per "16" != "8" inequality.  By adding count as a custom field type, the search would do a numeric comparison on the values and the search would succeed for "8 \textless= 16".
\item Added custom reservation statuses: "Starting", "Running", and "Stopping".  Each reservation status is shown as a different color in  the calendar view.
\item Added the ability to retrieve and set the reservation status from the Booked REST API.  	
\item Added the PRAGMA logo to the header.
\end{itemize}

@@

In the pilot implementation of the cloud scheduler  we made a lot of temporary assumptions, and  our future work will address them.  We will first work on integrating IPOP and PRAGMA-ENT into the cloud scheduler.  Next, we will rework the PCC software and integrate HTCondor so it's used in personal mode allowing us to keep a light footprint on each of the PRAGMA sites.  Finally, we will investigate using the CloudFront option in pragma\_boot to manage application virtual cluster images and staging them to each of the sites.     We will package and document the resulting software so that new users and sites can get quickly onto the PRAGMA cloud testbed and use it as an experimental service to test new science and infrastructure tools.

>>>>

\textbf{Developed a stub for managing virtual clusters:}  To provide an interface for managing virtual clusters, we used a simple stub to emulate the functionality of PCC.  The stub serves as a generic interface; it is a small Python script called \textit{pcc-check-reservations} that polls PRAGMA Booking via its REST interface and monitors reservations.  Once it finds a reservation that needs to be activated, it launches pragma\_boot via SSH.  It does not  monitor the virtual cluster nor does it email the users when their reservation are about to expire.

@@

\begin{itemize}
\item Added the ability to make multiple reservations on a resource per time slot to allow more than one virtual cluster to run simultaneously on a site.   This was the most extensive change we made to Booked.  Fortunately, no changes were needed to the backend database but it required several changes to the GUI code to allow an additional reservation to be made on a resource and to display multiple reservations per time slot in the calendar views.  In total, enhancements were made to seven PHP files and two template files.
\item Added a custom field for a public SSH key  to the user profile.  When PCC launches a virtual cluster, it pulls the public SSH key from the user's  profile and gives it to pragma\_boot so that the user can login as root once the virtual cluster is launched.   The ability to use a root login is not required for all but can be needed in some case if users want to do system modifications. A user with a root login has a full ownership of the virtual cluster. 
\item Added custom fields for CPU count, amount of memory per host, and virtual cluster image name to the reservation specification.
\item Added custom fields for CPU count, amount of memory per host, site hostname, and ENT capability (enabled, disabled) to the resource specification.
\item Added a numeric count as a custom field type.  Booked only provided text matching on search so if a host had 16 CPUs available and the user requested 8 CPUs, the search would fail per "16" != "8" inequality.  By adding count as a custom field type, the search would do a numeric comparison on the values and the search would succeed for "8 \textless= 16".
\item Added virtual cluster statuses: "Starting", "Running", and "Stopping".  Each virtual cluster status is shown as a different color in  the calendar view.  "Starting" means it has been approved and is being started up on the selected hypervisor... SHAVA EXPAND THIS
\item Added the ability to retrieve and set the reservation status from the Booked REST API.  	
\item Added the PRAGMA logo to the header.
\end{itemize}

@@

In the pilot implementation of the cloud scheduler  we made a lot of simplifying assumptions, and  our future work will address them.  NADYA TO PUT SENTENCES FOR REVIEWER 1.  In the future when we deploy on more sites, we can gather schedule statistics on usability and applicability of different scenarios.   We will also work on integrating IPOP and PRAGMA-ENT into the cloud scheduler.  Next, we will rework the PCC software and integrate HTCondor so it's used in personal mode allowing us to keep a light footprint on each of the PRAGMA sites.  Finally, we will investigate using the CloudFront option in pragma\_boot to manage application virtual cluster images and staging them to each of the sites.     We will package and document the resulting software so that new users and sites can get quickly onto the PRAGMA cloud testbed and use it as an experimental service to test new science and infrastructure tools.
